Reduced diversity and increased specialization of Alaska salmon fishermen:

### 2016-10-18 data/process_raw_data/process_raw_cfec_data.Rmd
updates to salmon and diversity

# drop records with no spp
cfec = cfec[-which(is.na(cfec$spec)),]
rm(spec.tbl)
```

@@

```{r}
cfec$p_holder = as.numeric(as.factor(cfec$p_holder))
cfec$cadfg = as.numeric(as.factor(cfec$cadfg))
cfec$p_serial = as.numeric(as.factor(cfec$p_serial))

>>>>

# drop records with no spp
cfec = filter(cfec, !is.na(spec))
rm(spec.tbl)
```

@@

```{r}
cfec$p_holder_id = cfec$p_holder

cfec$p_holder = as.numeric(as.factor(cfec$p_holder))
cfec$cadfg = as.numeric(as.factor(cfec$cadfg))
cfec$p_serial = as.numeric(as.factor(cfec$p_serial))

### 2016-10-18 salmon/paper/salmon_paper.Rmd
updates to salmon and diversity

seak = read.csv("salmon/data-generated/stopha_table32.csv")
pws = read.csv("salmon/data-generated/stopha_table33.csv")
kodiak = read.csv("salmon/data-generated/stopha_table35.csv")

@@

g6 = group_by(cfec[cfec$p_fshy=="S 03E" & cfec$spec %in% c("CHUM","COHO","SOCK","PINK","CHNK"),], year, spec, p_fshy) %>%
  summarize(p = sum(g_earn)) %>% group_by(year, p_fshy) %>% mutate(p = p/sum(p)) %>%
  ggplot(aes(year, p, group=spec, color = spec)) + geom_line() +  
  ylab("Species %") + xlab("") + ggtitle("S03E") + theme(legend.position="none")

@@

```{r, echo=FALSE, fig.pos="placeHere", fig.cap="Time varying intercepts on estimated mean revenue, by permit. These are interpreted as the mean change in revenue for each permit holder in each year (positive equates to increasing revenue, etc), after accounting for effects of catch diversification and days fished."}
# grab original data to look at permit names
diffdat = readRDS(file="../../portfolio/data-generated/salmon-diff-for-modeling.rds")
years = seq(min(diffdat$year), max(diffdat$year))
permits = levels(as.factor(diffdat$permit))

yearpermit = data.frame("yrpermit"=unique(diffdat$year_permit))
yearpermit$year = as.numeric(substr(yearpermit$yrpermit,1,4))
yearpermit$permit = substr(yearpermit$yrpermit,6,9)

load(paste0("../../salmon/analysis/",modelname,".Rdata"))

@@

```{r, fig.pos="placeHere", fig.cap="Time varying effects of adding 1 species on revenue (measured in ln dollars) for purse seine permit in Prince William Sound (S01E). This figure illustrates two things: (1) the benefit of adding more species diminishes as a function of past diversity, and (2) the economic benefit to adding more species has been reduced through time.", echo=FALSE, eval=FALSE}
# grab original data to look at permit names
diffdat = readRDS(file="../../salmon/data-generated/salmon.rds")
years = seq(min(diffdat$year), max(diffdat$year))
permits = levels(as.factor(diffdat$permit))

load(paste0("../../salmon/analysis/",modelname,".Rdata"))

@@

for(i in 1:nrow(df)) {
  tmp = x1[df$diversity[i]] * (est$b_1[,df$year[i], df$permit[i]])# + x2[df$diversity[i]] * (est$b_2[,df$year[i], df$permit[i]]+est$b2_str_yr_mu)
  df$pred[i] = median(tmp)
  df$low[i] = quantile(tmp,0.025)
  df$high[i] = quantile(tmp,0.975)
}
df_s01e_b1 = df
ggplot(df[df$permits=="S01E",], aes(x=x,y=pred,group=years)) +
  #geom_ribbon(aes(ymin=low,ymax=high), alpha=0.4) +
  geom_line() +
  facet_wrap(~years) + xlab("Previous species diversity") + ylab("Predicted benefit of adding +1 spp (ln $)")

@@

```{r, fig.pos="placeHere", fig.cap="Time varying effects of adding 1 species on revenue (measured in ln dollars) for hypothetical individuals with species diversity ~ 1. This shows declining benefits of diversification for most fisheries, S01M.", echo=FALSE}
# grab original data to look at permit names
diffdat = readRDS(file="../../portfolio/data-generated/salmon-diff-for-modeling.rds")
years = seq(min(diffdat$year), max(diffdat$year))
permits = levels(as.factor(diffdat$permit))

load(paste0("../../salmon/analysis/",modelname,".Rdata"))

@@

@@

```{r, fig.pos="placeHere", fig.cap="Time varying effects of adding 1 species on log standard deviation of revenue for hypothetical individuals with species diversity ~ 1.", echo=FALSE}
# grab original data to look at permit names
diffdat = readRDS(file="../../portfolio/data-generated/salmon-diff-for-modeling.rds")
years = seq(min(diffdat$year), max(diffdat$year))
permits = levels(as.factor(diffdat$permit))

load(paste0("../../salmon/analysis/",modelname,".Rdata"))

@@

df = expand.grid("year"=1:29, "diversity" = seq(1,length(x1)), "permit"=1:6)
df$permits = permits[df$permit]
df$years = years[df$year]
df$x = specdiv.prev[df$diversity]
df$pred = 0
df$low = 0
df$high = 0

@@

returns = readxl::read_excel("../../salmon/paper/salmon_returns_PWS.xlsx")
pinkPWS = returns[,c("Year", "Pink_total", "Chum_total")]
pinkPWS = pinkPWS[which(pinkPWS$Year >= 1985),]
pinkPWS$diff = c(NA, diff(log(pinkPWS$Pink_total)))

@@

# bring in slopes from above
slopes = df_s01e_b1[df_s01e_b1$permits=="S01E" & df_s01e_b1$diversity==1,]
slopes = slopes[,c("years","pred")]
names(slopes)[which(names(slopes)=="years")] = "Year"
names(slopes)[which(names(slopes)=="pred")] = "B1"
pinkPWS = dplyr::left_join(pinkPWS, slopes)

ggplot(data=pinkPWS, aes(b0, diff)) + geom_point() + stat_smooth(method=lm) + xlab("Estimated intercept from model") + ylab("Change in total pink salmon returns")

pinkPWS$diffchum = c(NA, diff(log(pinkPWS$Chum_total)))

prices = group_by(cfec[which(cfec$p_fshy%in%c("S 01E","S 03E") & cfec$spec%in%c("PINK","CHUM","SOCK")),], year, spec) %>% 
  summarize(meanPrice = mean(g_price)) %>%
  arrange(year)
prices <- dcast(melt(prices, id.vars = c("spec", "year")), year ~ variable+spec)
names(prices)[which(names(prices)=="year")]="Year"

pinkPWS = dplyr::left_join(pinkPWS, prices)
pinkPWS$pricediffchum = c(NA, diff(pinkPWS$meanPrice_CHUM))
pinkPWS$pricediffpink = c(NA, diff(pinkPWS$meanPrice_PINK))
pinkPWS$pricediffsock = c(NA, diff(pinkPWS$meanPrice_SOCK))

>>>>

seak = read.csv("../../salmon/data-generated/stopha_table32.csv")
pws = read.csv("../../salmon/data-generated/stopha_table33.csv")
kodiak = read.csv("../../salmon/data-generated/stopha_table35.csv")

@@

g6 = group_by(cfec[cfec$p_fshy=="S 03E" & cfec$spec %in% c("CHUM","COHO","SOCK","PINK","CHNK") & cfec$year > 0,], year, spec, p_fshy) %>%
  summarize(p = sum(g_earn)) %>% group_by(year, p_fshy) %>% mutate(p = p/sum(p)) %>%
  ggplot(aes(year, p, group=spec, color = spec)) + geom_line() +  
  ylab("Species %") + xlab("") + ggtitle("S03E") + theme(legend.position="none")

@@

```{r, echo=FALSE, fig.pos="placeHere", fig.cap="Time varying intercepts on estimated mean revenue, by permit. These are interpreted as the mean change in revenue for each permit holder in each year (positive equates to increasing revenue, etc), after accounting for effects of catch diversification and days fished."}
# grab original data to look at permit names
diffdat = readRDS(file="../../salmon/data-generated/salmon.rds")

years = seq(min(diffdat$year), max(diffdat$year))
permits = levels(as.factor(diffdat$permit))

# note that we have to use factor() here instead of unique() because
# that's the same as the ordering in the estimation code
yearpermit = data.frame("yrpermit"=levels(as.factor(diffdat$year_permit)))
yearpermit$year = as.numeric(substr(yearpermit$yrpermit,1,4))
yearpermit$permit = substr(yearpermit$yrpermit,6,9)

yearpermitold=yearpermit
load("../../salmon/analysis/model-linear.Rdata")
yearpermit=yearpermitold
est = extract(mod, permute="TRUE")

@@

```{r, echo=FALSE}
# fig.pos="placeHere", fig.cap="Time varying effects of adding 1 species on revenue (measured in ln dollars) for purse seine permit in Prince William Sound (S01E). This figure illustrates two things: (1) the benefit of adding more species diminishes as a function of past diversity, and (2) the economic benefit to adding more species has been reduced through time."
# grab original data to look at permit names
diffdat = readRDS(file="../../salmon/data-generated/salmon.rds")
years = seq(min(diffdat$year), max(diffdat$year))
#permits = levels(as.factor(diffdat$permit))

load("../../salmon/analysis/model-linear.Rdata")
yearpermit=yearpermitold

@@

for(i in 1:nrow(df)) {
  tmp = x1[df$diversity[i]] * (est$b_1[,df$year[i], df$permit[i]])# + x2[df$diversity[i]] * (est$b_2[,df$year[i], df$permit[i]]+est$b2_str_yr_mu)
  df$pred[i] = median(tmp)
  df$low[i] = quantile(tmp,0.025)
  df$high[i] = quantile(tmp,0.975)
}
df_s01e_b1 = df
#ggplot(df[df$permits=="S01E",], aes(x=x,y=pred,group=years)) +
#  #geom_ribbon(aes(ymin=low,ymax=high), alpha=0.4) +
#  geom_line() +
#  facet_wrap(~years) + xlab("Previous species diversity") + ylab("Predicted #benefit of adding +1 spp (ln $)")

@@

```{r, fig.pos="placeHere", fig.cap="Time varying effects of adding 1 species on revenue (measured in ln dollars) for hypothetical individuals with species diversity ~ 1. This shows declining benefits of diversification for most fisheries, S01M.", echo=FALSE}
# grab original data to look at permit names
diffdat = readRDS(file="../../portfolio/data-generated/salmon-diff-for-modeling.rds")
years = seq(min(diffdat$year), max(diffdat$year))
#permits = levels(as.factor(diffdat$permit))

yearpermitold=yearpermit
load("../../salmon/analysis/model-linear.Rdata")
yearpermit=yearpermitold

@@

df = expand.grid("year"=1:length(years), "diversity" = seq(1,length(x1)), "permit"=1:6)
df$permits = permits[df$permit]
df$years = years[df$year]
df$x = specdiv.prev[df$diversity]
df$pred = 0
df$low = 0
df$high = 0
b0_indx = match(paste(as.character(df$years), as.character(df$permits)), as.character(yearpermit$yrpermit))

@@

```{r, fig.pos="placeHere", fig.cap="Time varying effects of adding 1 species on log standard deviation of revenue for hypothetical individuals with species diversity ~ 1.", echo=FALSE}
# grab original data to look at permit names
diffdat = readRDS(file="../../portfolio/data-generated/salmon-diff-for-modeling.rds")
years = seq(min(diffdat$year), max(diffdat$year))
#permits = levels(as.factor(diffdat$permit))

load("../../salmon/analysis/model-linear.Rdata")
yearpermit=yearpermitold

@@

df = expand.grid("year"=1:length(years), "diversity" = seq(1,length(x1)), "permit"=1:6)
df$permits = permits[df$permit]
df$years = years[df$year]
df$x = specdiv.prev[df$diversity]
df$pred = 0
df$low = 0
df$high = 0

@@

returns = readxl::read_excel("../../salmon/paper/salmon_returns_PWS.xlsx")
pinkPWS = returns[,c("Year", "Pink_total", "Chum_total")]
pinkPWS = pinkPWS[which(pinkPWS$Year >= 1975),]
pinkPWS$diff = c(NA, diff(log(pinkPWS$Pink_total)))

@@

ggplot(data=pinkPWS, aes(b0, diff,color=Year)) + geom_point() + stat_smooth(method=lm) + xlab("Estimated intercept from model") + ylab("Change in total pink salmon returns")

# bring in slopes from above
#slopes = df_s01e_b1[df_s01e_b1$permits=="S01E" & df_s01e_b1$diversity==1,]
#slopes = slopes[,c("years","pred")]
#names(slopes)[which(names(slopes)=="years")] = "Year"
#names(slopes)[which(names(slopes)=="pred")] = "B1"
#pinkPWS = dplyr::left_join(pinkPWS, slopes)

#pinkPWS$diffchum = c(NA, diff(log(pinkPWS$Chum_total)))

#prices = group_by(cfec[which(cfec$p_fshy%in%c("S 01E","S 03E") & #cfec$spec%in%c("PINK","CHUM","SOCK")),], year, spec) %>% 
#  summarize(meanPrice = mean(g_price)) %>%
#  arrange(year)
#prices <- dcast(melt(prices, id.vars = c("spec", "year")), year ~ #variable+spec)
#names(prices)[which(names(prices)=="year")]="Year"

#pinkPWS = dplyr::left_join(pinkPWS, prices)
#pinkPWS$pricediffchum = c(NA, diff(pinkPWS$meanPrice_CHUM))
#pinkPWS$pricediffpink = c(NA, diff(pinkPWS$meanPrice_PINK))
#pinkPWS$pricediffsock = c(NA, diff(pinkPWS$meanPrice_SOCK))
